---
title: "Lab 10"
author: "Ruixuan Hu"
date: "11/22/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1. Write a function that calculates cumulative distribution function of a binomial random variable. Compare results from your function with pbinom() function.

```{r}
cdf<- function(q,n,π) {
count=0
  for (i in 1:q) {
    Pri=choose(n,i)*(π^i)*((1-π)^(n-i)) 
    count=count+Pri
  }
return(count)
}

cdf(2,6,0.5)
pbinom(2,6,0.5)
cdf(3,7,0.6)
pbinom(3,7,0.6)
```

From the result above, we can figure out that the results are really similar.
  



2. Write a function that runs simulations to obtain power from a one-sample t-test. Run your function (with number of simulations = 10,000 ) with n = 30, delta = 0.5, sd = 1 and sig.level = 0.05. Compare your results with power.t.test(n = 30, delta = 0.5, sd = 1, sig.level = 0.05, type = ‘one.sample’).


First, turn my simulations to a function.
```{r}
PowerSim <- function(n,delta,sd,sig.level) {
  data<-data.frame(num=rnorm(n=n,mean = 3,sd=sd))
  Sim<- t.test(data$num,mu=3+delta)
  return(Sim$p.value)
 
}
PowerSim(30,0.5,1,0.05)
```

Now replicate the simulation 10000 times.
```{r}
set.seed(12345)
my_reps <- replicate(10000,PowerSim(30,0.5,1,0.05))
  aplha=sig.level=0.05
  power <- mean(my_reps < aplha)
  power

```
So from my outcome, the result is 0.7492. Let us then use power.t.test.
```{r}
power.t.test(n = 30, delta = 0.5, sd = 1, sig.level = 0.05, type = "one.sample")
```

As we can see, the power power.t.test calculates is 0.7540. From the result above, we can figure out that the results are really similar.